%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.2 (25/3/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage[scale=0.8]{geometry} % Reduce document margins

%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\providecommand\BibTeX{{B\kern-.05em{\textsc{\textsf{i\kern-.025em b}}}\kern-.08em\TeX}}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Vedran} % Your first name
\familyname{Šego} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{3 Six Bells Lane}{TN131JE, Sevenoaks, UK}
\mobile{(44) 77-9592-9136}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{vsego@vsego.org}
\homepage{vsego.org}{vsego.org} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{vsego} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
\quote{\hskip7mm``It’s a magical world, Hobbes, ol' buddy\dots\newline{}Let's go exploring!'' -- Calvin}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-3] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

\section{Summary}

\cvitem{}{A mathematician, an experienced software developer, and a Linux power user, with over a decade of experience in academic research and teaching.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2006--2009}{PhD in numerical linear algebra}{The University of Zagreb}{Zagreb, Croatia}{}{}  % Arguments not required can be left empty
\cventry{2001--2006}{Magister Scientiae (MPhil equivalent) in mathematics}{The University of Zagreb}{Zagreb, Croatia}{}{}
\cventry{1995--2000}{Graduate engineer (MSc equivalent) in mathematics}{The University of Zagreb}{Zagreb, Croatia}{Major: Computer science, graduated in top 10\% of my class}{}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Highlights}

\cventry{2015}{One day Python course}{NAG (Numerical Algorithms Group Ltd)}{Manchester}{}{
    \begin{itemize}
        \item One day intensive course on Python, aimed at NAG's experienced programmers.
        \item Covered topics ranging from the very basics of Python up to advanced topics (emulating MATLAB via SciPy, unit testing, interfacing C and FORTRAN, and OOP).
        \item Prepared Jupyther materials, specifically tailored for NAG, and delivered them in form of an interactive workshop.
        \item The course received \textbf{high praise} from all the participants.
    \end{itemize}
}

\cventry{2015}{Lecturer\! for\! \emph{Programming\! with\! Python}}{The\! University\! of\! Manchester}{Manchester,\! UK}{}{
    \begin{itemize}
        \item One semester course on programming with Python, aimed at mathematics students with no prior programming experience.
        \item Prepared \href{https://github.com/vsego/python-lecture-notes}{IPython materials}; topics ranging from the basics of programming up to moderately advanced concepts, with some additional topics for the students who wanted to learn more (complexity of algorithms, Matplotlib, NetworkX, PIL).
        \item Delivered weekly lectures and lab classes to a group of 50 students.
        \item Designed and marked weekly tests and a project-based final exam.
        \item The feedback was generally positive, and the course \textbf{continues to be taught} at the University following my materials.
    \end{itemize}
}

\cventry{2007-present}{On-line homework generator and verifier}{The University of Zagreb}{Zagreb, Croatia}{}{
    \begin{itemize}
        \item Designed, coded, and maintained a fully automated PHP engine for generating students' homework assignments and marking their uploaded source codes and other solutions, currently used for programming courses and numerical mathematics.
    \end{itemize}
}

\cventry{2002--present}{Linux servers administrator}{The University of Zagreb}{Zagreb, Croatia}{}{
    \begin{itemize}
        \item Installed and maintained several research, web, and mail servers, mostly under RedHat Linux, later replaced by Fedora; some under Debian.
    \end{itemize}
}

\subsection{Vocational}

\cventry{2012--2015}{Research visitor}{The University of Manchester}{Manchester, UK}{}{
    \begin{itemize}
        \item Visited Prof.\ Françoise Tisseur in the Numerical Linear Algebra group.
        \item Participated in research activities, co-organized a conference, delivered seminars and presentations on various topics to different audiences.
        \item Developed \href{https://github.com/vsego/shrinking}{\texttt{shrinking}}, a Python module supporting my research on repairing correlation matrices.
        \item Proposed and created \emph{Programming with Python}\/ course.
        \item Designed and coded \textit{Coursework marker}, a program for semi-automatic marking of students' final project.
    \end{itemize}
}

\cventry{2001--2012}{Research associate}{The University of Zagreb}{Zagreb, Croatia}{}{
    \begin{itemize}
        \item Participated in research activities and presented my results at international conferences.
        \item Taught, marked, and prepared materials for \textit{Programming in C}, \textit{Web programming}, \textit{Data structures and algorithms}, \textit{Programming in Pascal}, and general computer courses.
        \item Wrote a two-part manuscript for \textit{Programming in C}, which is still the official manuscript.
        \item Mentored students working on web programming projects and numerical mathematics.
        \item Developed \href{ttp://decision.math.hr/download/MetPot.zip}{\textit{MetPot}} and \href{http://decision.math.hr/download/Decision.zip}{\textit{Decision}}, applications supporting my research in decision theory.
    \end{itemize}
}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2000}{The University of Zagreb Rector's award for the joint work \textit{Multicriteria decision making} with R.~Piskač, under the guidance of Associate professor L.~Čaklović.}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Programming}{Python, Django, PHP, HTML, CSS, JavaScript, jQuery, jQuery UI, Scriptish, Perl, C, bash
shell scripting, SQL, MySQL, ImageMagick, MATLAB, Mathematica.}
\cvitem{Productivity}{\LaTeX, \BibTeX, Beamer, Vim/Gvim, GIMP, Inkscape, GitHub, LibreOffice, MS Office.}
\cvitem{OS}{Linux (power user), Microsoft Windows, HP-UX.}

%----------------------------------------------------------------------------------------
%	FUN PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Fun projects}

\cvitem{\href{http://github.com/vsego/PyteArt}{PyteArt}}{Collection of generators of ASCII art with overlapping characters, written in Python.}
\cvitem{\href{http://amaze.vsego.org/}{aMaze}}{JavaScript labyrinth game.}
\cvitem{\href{http://vsego.org/minesweeper/}{Minesweeper}}{Version of the classic game written as a JavaScript class.}
\cvitem{\href{http://mapodic.vsego.org/}{MaPoDic}}{Matrix polynomials dictionary, written in PHP and jQuery.}
\cvitem{\href{http://travian.vsego.org/}{vTU}}{Set of utilities for MMORPG \href{http://www.travian.com/}{Travian}, written in PHP.}
\cvitem{\href{http://pirates.vsego.org/}{Pirates}}{Set of utilities for MMORPG \href{https://www.kabam.com/games/pirates-tides-of-fortune/}{Pirates: Tides of Fortune}, written in PHP.}
\cvitem{SlowSorts}{Two algorithms, opposite of QuickSort.}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}
%
%%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
%
%\cvlistdoubleitem{web-based MMORPGs}{films}
%\cvlistdoubleitem{photography}{hiking}
%%\cvlistitem{Running}

%----------------------------------------------------------------------------------------
%	VOLUNTEERING SECTION
%----------------------------------------------------------------------------------------

\section{Volunteering}

\cventry{2013-present}{Member of Stack Exchange}{}{}{}{
    \begin{itemize}
        \item Among top 5\% users on Mathematics (for undergraduate and graduate mathematics), top 7\% on CodeReview (for people wanting to improve their already working programs), top 4\% on Movies, and I occasionally participate on StackOverflow (for programming inquiries).
    \end{itemize}
}
\cventry{2012-2013}{Webmaster}{\href{http://www.maths.manchester.ac.uk/~siam/}{Manchester SIAM Student Chapter}}{Manchester, UK}{}{}
\cventry{2002-present}{Forum administrator}{The University of Zagreb}{Zagreb, Croatia}{}{
    \begin{itemize}
        \item Installed and maintained ``\href{http://degiorgi.math.hr/forum/}{Forum@DeGiorgi}'', a web forum aimed at helping mathematics students.
        \item Made many significant code changes.
    \end{itemize}
}

%----------------------------------------------------------------------------------------

\end{document}
